\section{DOM-Bench Task Suite Details}
\label{app:task_suite} % Label for referencing

This appendix provides specific examples of tasks within the DOM-Bench suite, categorized by tier. Each task contributes to evaluating the capabilities outlined in Section 2.2 (Benchmark Design).

\subsection{Tier 1: Fundamentals}
\begin{itemize}
    \item \textbf{Focus:} Core shape control, manipulation primitives.
    \item \textbf{Environment:} Primarily Simulation (e.g., SoftGym, DaXBench).
    \item \textbf{Evaluation Targets:} Basic manipulation success, shape accuracy, efficiency.
    \item \textbf{Minimum Requirement Tasks:}
        \begin{itemize}
            \item \texttt{Cloth Fold (Single)}: Fold a square cloth along a central axis. \textit{Targets: Shape control. Metrics: Fold alignment error, final shape IoU.}
            \item \texttt{Cloth Spread}: Unfold a crumpled cloth to maximize coverage. \textit{Targets: Shape control. Metrics: Coverage area (\%), wrinkle score.}
            \item \texttt{Rope Straighten}: Make a curved rope straight. \textit{Targets: Shape control. Metrics: Final end-to-end distance / rope length ratio, curvature.}
            \item \texttt{Liquid Pour (Simulated)}: Pour a target volume between containers. \textit{Targets: State control. Metrics: Volume accuracy, spillage amount.}
            \item \texttt{Elastic Stretching (Simulated)}: Stretch a band to a target length. \textit{Targets: Shape control under tension. Metrics: Target length accuracy.}
        \end{itemize}
    \item \textbf{Stretch Goal Tasks:}
        \begin{itemize}
            \item \texttt{Sponge Compression (Simulated)}: Compress a block to target dimensions. \textit{Targets: Shape control under force. Metrics: Dimension accuracy.}
        \end{itemize}
\end{itemize}

\subsection{Tier 2: Complex Interactions}
\begin{itemize}
    \item \textbf{Focus:} Multi-step sequences, tool use, constrained motion, basic object interactions.
    \item \textbf{Environment:} Simulation (Garment Lab) and Real-World (RPL Lab).
    \item \textbf{Evaluation Targets:} Task completion, planning, interaction quality, constraint adherence.
    \item \textbf{Minimum Requirement Tasks:}
        \begin{itemize}
            \item \texttt{Hang Clothes (Sim)}: Place a cloth item onto a hanger. \textit{Targets: Multi-step manipulation, object interaction. Metrics: Success rate, stability.}
            \item \texttt{Wash in Sink (Sim)}: Simulate wiping/scrubbing an object in a sink area. \textit{Targets: Tool use (implicit sponge), coverage. Metrics: Coverage area, cycle consistency.}
            \item \texttt{Object Wrapping (Real)}: Wrap a simple rigid object (e.g., box) with paper/cloth. \textit{Targets: Multi-step manipulation, surface following. Metrics: Success rate, coverage quality, wrapping tightness (qualitative).}
            \item \texttt{Knot Tying (Simple, Real)}: Tie an overhand knot in a rope. \textit{Targets: Topological manipulation. Metrics: Success rate, knot correctness (topological check).}
            \item \texttt{WashWithSponge (Real)}: Use a sponge to wipe a designated area. \textit{Targets: Tool use, coverage. Metrics: Success rate, area coverage percentage.}
            \item \texttt{Spreading Viscous Material (Real)}: Spread simulated paste/dough on a surface with a tool. \textit{Targets: Tool use, distribution control. Metrics: Success rate, coverage uniformity.}
        \end{itemize}
    \item \textbf{Stretch Goal Tasks:}
        \begin{itemize}
            \item \texttt{Knot Untying (Simple, Real)}: Untie a specific simple knot. \textit{Targets: Inverse manipulation, state recognition. Metrics: Success rate.}
            \item \texttt{Surgical Suturing (Simplified, Real)}: Pass a needle/thread through marked points on phantom skin. \textit{Targets: Fine manipulation, precision, tool use. Metrics: Success rate, point accuracy, stitch regularity.}
            \item \texttt{Store In Closet (Sim)}: Fold a cloth item and place it in a designated shelf area. \textit{Targets: Long-horizon (implicit), combined skills. Metrics: Success rate, placement accuracy.}
        \end{itemize}
\end{itemize}

\subsection{Tier 3: Foundation Model Evaluation}
\begin{itemize}
    \item \textbf{Focus:} Language understanding, reasoning, planning, generalization, adaptation specifically for VLAs.
    \item \textbf{Environment:} Primarily Real-World (RPL Lab).
    \item \textbf{Evaluation Targets:} Instruction following fidelity, planning success, generalization capability, ambiguity resolution.
    \item \textbf{Minimum Requirement Tasks (Language-Conditioned):}
        \begin{itemize}
            \item \texttt{Complex Placement}: "Place the \textbf{folded blue} napkin \textbf{directly on top of} the placemat, \textbf{aligned with the bottom edge}." \textit{Targets: Language (spatial, relational, attributes). Metrics: Constraint satisfaction accuracy.}
            \item \texttt{Precise Action}: "Pour \textbf{exactly 50ml} of the liquid (use rice/beans for real-world safety) \textbf{slowly} into the \textbf{tallest} container." \textit{Targets: Language (quantity, parameters, attributes). Metrics: Parameter accuracy (volume, qualitative rate), target selection correctness.}
            \item \texttt{Ordered Arrangement}: "Arrange the \textbf{three different colored} ropes \textbf{parallel} to each other, ordered \textbf{red, green, blue} from left to right." \textit{Targets: Language (multi-object, spatial, ordering). Metrics: Arrangement accuracy (parallelism, order).}
            \item \texttt{Goal-Oriented Constraint}: "Fold the t-shirt \textbf{so the logo on the front is hidden}." \textit{Targets: Language (goal constraint), reasoning. Metrics: Goal satisfaction success rate.}
        \end{itemize}
    \item \textbf{Minimum Requirement Tasks (Long-Horizon Planning):}
        \begin{itemize}
            \item \texttt{Laundry Prep}: "Prepare the laundry: \textbf{separate the whites from the colors} (use distinct cloth types), then \textbf{fold the towels} and \textbf{place the shirts} in the basket." \textit{Targets: Planning, sequencing, multi-skill execution. Metrics: Sub-goal completion, overall success rate.}
            \item \texttt{Packing}: "\textbf{Fold two shirts, one pair of pants, and three pairs of socks}, then \textbf{arrange them neatly} in the small suitcase." \textit{Targets: Planning, multi-object folding, spatial arrangement. Metrics: Success rate, packing density (qualitative), item integrity.}
            \item \texttt{Bandage Prep}: "\textbf{Unroll the gauze}, \textbf{cut a 15cm strip} (robot indicates cut point, human assists/simulates cut if needed), and \textbf{fold it into a square pad}." \textit{Targets: Planning, tool interaction (simulated/assisted), sequencing. Metrics: Sub-goal completion, final state accuracy.}
        \end{itemize}
    \item \textbf{Minimum Requirement Tasks (Generalization):}
        \begin{itemize}
            \item \texttt{Open-Vocabulary Object}: "Fold the \textbf{power cable}" (vs. trained ropes/cloth). \textit{Targets: Object generalization. Metrics: Success rate on unseen object categories.}
            \item \texttt{Open-Vocabulary Action/Shape}: "Arrange the rope to form the \textbf{letter 'Q'}." or "Use the sponge to \textbf{wipe} the surface clean." \textit{Targets: Action/shape generalization. Metrics: Novel task success rate, qualitative shape/action match.}
            \item \texttt{Instruction Generalization}: "\textbf{Tidy up} the pile of clothes." (vs. explicit fold/stack commands). \textit{Targets: Instruction robustness. Metrics: Success rate with paraphrased/abstract instructions.}
        \end{itemize}
    \item \textbf{Stretch Goal Tasks:}
        \begin{itemize}
            \item \texttt{Creative/Complex Shaping}: "Tie the two ropes together using a \textbf{bow knot}." or "Shape the play-doh into a \textbf{recognizable animal}." \textit{Targets: Advanced generalization, complex manipulation. Metrics: Qualitative assessment, knot/shape correctness.}
            \item \texttt{Ambiguity Handling}: Give ambiguous command like "Prepare the rope." \textit{Targets: Reasoning, potential for clarification query. Metrics: Action plausibility, query generation rate (if applicable).}
            \item \texttt{Error Recovery (Prompted)}: Induce failure (e.g., drop object) and instruct: "You dropped it, pick it up and continue." \textit{Targets: Adaptation, planning repair. Metrics: Recovery success rate.}
        \end{itemize}
\end{itemize}